{\cis}: A Python Package for Integrating Computational Models Across Languages and Scales

### 2018-10-23 papers/lang2018/ms.tex
Minor edit

\ifieee
	\begin{IEEEkeywords}
		Plant modeling, Modeling, Communication
	\end{IEEEkeywords}
	\IEEEpeerreviewmaketitle
\else
	\maketitle
\fi

@@

%---------------------------------------------------------------------------------
%---------------------------------------------------------------------------------
% BACKGROUND
\section{Background}\label{S:background}
%
Computational plant models are usually written with a very specific research question in mind. The resulting programs are highly tuned for one purpose and written specifically for scientists within an isolated group of collaborators. Scientists will generally write programs in the language they are most familiar with and, given that there is no consensus on one programming language as ideal for all scientific applications, the language will often vary between research groups, if not between members within the groups themselves. The same can be said of data formats which can be highly tailored to the target question and may or may not include metadata like the data types, field names, or units. To integrate two biological models like the root and shoot models from \S\ref{S:intro}, the following questions must be addressed:
%
\begin{enumerate}
	\item Orchestration: How will models be executed?
	\item Communication: How will information be passed from one model to the next across languages?
	\item Translation: How will data output by one model be translated into a format understood by the next model?
\end{enumerate}

>>>>

\ifieee
	\begin{IEEEkeywords}
		Plant Modeling, Modeling, Communication, Computational Framework, Model Integration, Parallel Processing
	\end{IEEEkeywords}
	\IEEEpeerreviewmaketitle
\else
	\maketitle
\fi

@@

%---------------------------------------------------------------------------------
%---------------------------------------------------------------------------------
% BACKGROUND
\section{Background}\label{S:background}
%
Computational plant models are usually written with a very specific research question in mind. The resulting programs are highly tuned for one purpose and written specifically for scientists within an isolated group of collaborators. Scientists will generally write programs in the language they are most familiar with and, given that there is no consensus on one programming language as ideal for all scientific applications, the language will often vary between research groups, if not between members within the groups themselves. The same can be said of data formats which can be highly tailored to the target question and may or may not include metadata such as the data types, field names, or units. To integrate two biological models like the root and shoot models from \S\ref{S:intro}, the following questions must be addressed:
%
\begin{enumerate}
	\item Orchestration: How will models be executed?
	\item Communication: How will information be passed from one model to the next across languages?
	\item Translation: How will data output by one model be translated into a format understood by the next model?
\end{enumerate}
